---
output: github_document
---

# SDI (Score Decompostion Inference)

An R package to quantify the sampling uncertainty of Bregman type score decomposition. 

## Installation 

Development version: the  current version is available from GitHub.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("marius-cp/SDI")
```



## Example 

* The following is based on the inflation application in the paper **Robust Mean Forecast Evaluation with Score Decompositions**; see [GitHub repository](https://github.com/marius-cp/chapter5phdthesis). Link to the paper (to be included).

```{r example1, warning=F, message=F}
library(SDI)

url <- "https://raw.githubusercontent.com/marius-cp/chapter5phdthesis/main/02_application/inflation/murphy_replication/inflation_mean.rds"
dat <- readRDS(url(url)) %>%
  dplyr::filter(stemp_rlz <= "2020-12-01")
```

* Apply the SDI function:

```{r example2, warning=F, message=F}
sdi <- 
  SDI(
  X_1 = dat$michigan, 
  X_2 = dat$spf, 
  Y = dat$rlz, 
  S = function(x,y) (x-y)^2, 
  V = function(x,y) (x-y)*2, 
  Spp = function(x,y) 2
)
```


* Extract the score decomposition for the Michigan and SPF forecasts:

```{r example3, warning=F, message=F}
sdi$asyvardm$dec_1 # michigan
sdi$asyvardm$dec_2 #spf
```

* Extract the p-values of test for equal scores, equal miscalibration and equal discrimination:

```{r example4, warning=F, message=F}
sdi$asyvardm$pvals
```


